Exploratory Data Analysis

### 2023-11-03 analysis/eda.qmd
Update eda.qmd

left_right_regression <- function(name, var, family) {
  name <- glm(
    {{ var }} ~ ich_laterality + age + ich_location + gcs_baseline + ich_volume_baseline + ivh + time_symptoms_to_ed,
    data = data_erich_atach,
    family = family
  )

  neurosurgery_glm |>
    tbl_regression(
      exponentiate = TRUE,
      include = ich_laterality
    )
}

>>>>

left_right_regression <- function(name, x, family) {
  name <- glm(
    {{ x }} ~ ich_laterality + age + ich_location + gcs_baseline + ich_volume_baseline + ivh + time_symptoms_to_ed,
    data = data_erich_atach,
    family = family
  )

  {{ x }} |>
    tbl_regression(
      exponentiate = TRUE,
      include = ich_laterality
    )
}
